---
output:
  word_document: default
  html_document: default
---
##R Studio Refresher Assignment 
##Michelle McBride BAN 502 Aug 2024

```{r}
library(tidyverse)
```

##Number of Rows and Columns in Diamond Dataframe

```{r}
diamonddata=diamonds
nrow(diamonddata)
ncol(diamonddata)
```

##Question 1 & 2: There are 53,940 rows and 10 columns in the data frame. 

```{r}
ggplot(data=diamonddata,aes(x=carat,y=price))+
  geom_point()
```
##Question 3: As the carats increase, so does the price. 

```{r}
ggplot(data=diamonddata,aes(x=carat,y=price, color=cut))+
  geom_point()
```
##As cut increases, price does not change. 

```{r}
ggplot(data=diamonddata,aes(x=carat,y=price, color=cut))+
  geom_point()+
  facet_grid(color~.)
```
## Question 5: Faceting provided a seperate plot for each color. 

```{r}
library(readr)
Inventory <- read_csv("InventoryData.csv")
mean(Inventory$`On Hand`)
```

##Question 6: In the inventory data frame supplier is a character. 
##Question 7: The mean of On Hand is 100.5373

```{r}
InventoryA <-Inventory%>%
  filter(Supplier=="A")
```

```{r}
InventoryA=mutate(InventoryA,OnHandRatio=`On Hand`/`Annual Demand`)
```

```{r}
Avg_Cost<-InventoryA%>%group_by(`Item SKU`)%>%
  summarise(SKUAvgCost=mean(`Cost per Unit ($)`),.groups = 'drop')%>%
  as.data.frame()
```

##Question 10: Avg cost of 011 is 12.33000