---
title: "Module2Assignment2"
author: "Michelle McBride"
date: "2024-09-06"
output:
  word_document: default
  html_document:
    df_print: paged
---
```{r}
library(readr)
bike_cleaned_3 <- read_csv("bike_cleaned-3.csv")
bike=bike_cleaned_3

library(tidyverse)
bike=bike%>%mutate(dteday=mdy(dteday))

bike=bike%>%mutate_if(is.character,as_factor)

bike=bike%>%mutate(hr = as.factor(hr))
```


```{rcormatrix}

```

## Question 1: Temp has the highest coorelation 

```{rcormatrix}
ggpairs(bike, columns = c("windspeed", "hum","atemp", "temp","count"))
```

## Temp is still the most strongly coorelated

```{r}
ggplot(bike,aes(x=hr,y=count)) + geom_boxplot()
```


```{r}
ggplot(bike,aes(x=season,y=count)) + geom_boxplot()
```

## Question 2: Summer has the highest count of rides. 

## Build model to predit how hour affects count
```{rmodelbuild}
bike_recipe=recipe(count~hr,bike)

lm_model = #give the model type a name 
  linear_reg() %>% #specify that we are doing linear regression
  set_engine("lm") #specify the specify type of linear tool we want to use 

lm_wflow = 
  workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(bike_recipe)

lm_fit = fit(lm_wflow, bike)

summary(lm_fit$fit$fit$fit)
```

#Question 3: There are 22 dummy variables. 
#Question 4: Hour 0 is the base level category - it does not have a slope in the model. 
#Question 5: Hour 17 has the highest number of rides. 

```{r}
ggplot(bike, aes(x=temp, y=count)) + geom_point()
```


#Question 6: The scatterplot suggests that as temp increases so does the number of rides. 

#Now use a linear regression model with multiple variables and modify the original recipe to do it. 
```{rbikerecipe2}
bike2_recipe = recipe(count ~ hr + temp, bike)

lm_model = #give the model type a name 
  linear_reg() %>% #specify that we are doing linear regression
  set_engine("lm") #specify the specify type of linear tool we want to use 

lm_wflow = 
  workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(bike2_recipe)

lm_fit2 = fit(lm_wflow, bike)

summary(lm_fit2$fit$fit$fit)
```

#Question 7: slope of hr23 is 31.748
#Question 8: 0.5891

```{rbikerecipe3}
bike3_recipe = recipe(count ~ temp + atemp, bike)

lm_model = #give the model type a name 
  linear_reg() %>% #specify that we are doing linear regression
  set_engine("lm") #specify the specify type of linear tool we want to use 

lm_wflow = 
  workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(bike3_recipe)

lm_fit2 = fit(lm_wflow, bike)

summary(lm_fit2$fit$fit$fit)
```

#Question 9: 0.1639
#Question 10: Both temp and atemp are significant 
#Question 11: 

```{r}
bike4=bike %>% dplyr::select("count","season","mnth","hr","holiday","weekday","workingday","weathersit","temp","atemp","hum","windspeed")
```

```{r}
allmod = lm(count ~., bike4) #use the ~. to include all predictors rather than typing them all in
summary(allmod)

emptymod = lm(count ~1, bike4) #use ~1 to build an empty model 
summary(emptymod)
```

#Question 12: Weekday and holiday make up workday and so NA appears in the analysis.

#backward stepwise
```{rbackstep}
#backward
backmod = stepAIC(allmod, direction = "backward", trace = TRUE) #trace = TRUE shows how the model is built (which variables are removed)
summary(backmod)
```

# Questoin 13: Workingday is removed in the backward stepwise
